---
title: "Text Analysis"
output: html_notebook
---

Reading the file into R and using only the terms Description and Deal as variable.
```{r}
vc=read.csv("Dataset.csv",stringsAsFactors = F)
vc=vc[,c(1,2)]
vc$deal=as.factor(vc$deal)
str(vc)
table(vc$deal)
vc$Deal=ifelse(vc$deal==F,0,1)
vc=vc[,c(2,3)]
```

Creating a corpus with the varibale description for cleaning the data and then creating Document term matrix with the varible Deal as DV.
```{r}
library(tm)
library(SnowballC)


corpus = VCorpus(VectorSource(vc$description))
corpus = tm_map(corpus, content_transformer(tolower))
as.character(corpus[[60]])
corpus = tm_map(corpus, removeNumbers)
as.character(corpus[[60]])
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, removeWords, stopwords("english"))
as.character(corpus[[60]])
corpus = tm_map(corpus, stemDocument)
as.character(corpus[[60]])
corpus = tm_map(corpus, stripWhitespace)
as.character(corpus[[60]])

dtm = DocumentTermMatrix(corpus)
dtm = removeSparseTerms(dtm, 0.999)
dataset = as.data.frame(as.matrix(dtm))
dataset$Deal=vc$Deal

dataset$Deal = factor(dataset$Deal, levels = c(0,1))

```

using the data frame created to predict the Deal by using CART.
```{r}
library(caTools)
set.seed(123)
split = sample.split(dataset$Deal, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)

library(rpart)
library(rpart.plot)
library(rattle)
library(caret)
cart = rpart(Deal~ ., data=training_set, method="class")
cart

#Plot the CART model
prp(cart,extra=2)

fancyRpartPlot(cart)
printcp(cart)
plotcp(cart)

cr1=prune(cart,cp=0.031)
cr1
fancyRpartPlot(cr1)

predictCART = predict(cart, newdata=test_set[-3465],type="class")

confusionMatrix(test_set$Deal,data=predictCART,positive="1")
```

using the data frame created to predict the Deal by using Random Forest.

```{r}
library(randomForest)
set.seed(123)
crf = randomForest(x = training_set[-3465],
                   y = training_set$Deal,
                   ntree = 100, mtry=15)

#Plot a chart of variable importance in a random forest
varImpPlot(crf)

# Make predictions:
predictRF = predict(crf, newdata=test_set[-3465],type="class")

#Confusion matrix
confusionMatrix(test_set$Deal,data=predictRF,positive="1")
```

using the data frame created to predict the Deal by using logistic regression.

```{r}
log=glm(Deal~.,data=training_set,family = binomial)

# Make predictions:
logi = predict(log, newdata=test_set[-3465],type="response")
Log = table(test_set$Deal, logi > 0.5)
Log
#####Accuracy
(Log[1,1]+Log[2,2])/nrow(test_set)
```

Adding a derived variable Ratio=asked for/valuation and rebuilding the models built above.

```{r}
vc=read.csv("Dataset.csv",stringsAsFactors = F)
vc$Ratio=round(vc$askedFor/vc$valuation,2)

vc=vc[,c(1,2,20)]
vc$deal=as.factor(vc$deal)
str(vc)
table(vc$deal)
vc$Deal=ifelse(vc$deal==F,0,1)
vc=vc[,c(2,3,4)]


dataset$Ratio=vc$Ratio
dataset$Deal = factor(dataset$Deal, levels = c(0,1))

```

Running Randon CART.
```{r}
set.seed(1234)
split = sample.split(dataset$Deal, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)

cart = rpart(Deal~., data=training_set, method="class")
cart

#Plot the CART model
prp(cart,extra=2)



predictCART = predict(cart, newdata=test_set,type="class")

confusionMatrix(test_set$Deal,data=predictCART,positive="1")
```

Running a random forest.

```{r}
crf = randomForest(x = training_set[-3465],
                   y = training_set$Deal,
                   ntree = 100, mtry=15)

#Plot a chart of variable importance in a random forest
varImpPlot(crf)

# Make predictions:
predictRF = predict(crf, newdata=test_set[-3465],type="class")

#Confusion matrix
confusionMatrix(test_set$Deal,data=predictRF,positive="1")
```

Running a logistic regression model.

```{r}
log=glm(Deal~.,data=training_set,family = binomial)

# Make predictions:
logi = predict(log, newdata=test_set[-3465],type="response")
Log = table(test_set$Deal, logi > 0.5)
Log
#####Accuracy
(Log[1,1]+Log[2,2])/nrow(test_set)
```


